First looks at RF and MI

### 2024-08-06 pr_ml/240804_initial_RF.Rmd
update ugly formatting

@@

**Initial thoughts - Region**
 - looks like region was correctly predicted for all data
 - NO3 as the most important seems sensible, a little surprised it wasn't salt-related though
 - white noise near bottom (transect does not contribute more than random noise to the model so we should ignore it here)

@@

**Initial thoughts - Transect**
 - all but one correctly classified (one Transition looked like Upland)
 - sulfate is interesting, maybe the relative transition in redox is more consistent than the relative transition in other things across CB and WLE sites
 - neither horizon nor region is important to this model

@@

**Initial thoughts - Site**
 - All correctly identified

>>>>

Note that I'm adding a white noise variable to all models. That's there as a guide for interpreting which variables are contributing more to the model than random chance.

@@

**Initial thoughts - Region**

  - looks like region was correctly predicted for all data 
  - NO3 as the most important seems sensible, a little surprised it wasn't salt-related though 
  - white noise near bottom (transect does not contribute more than random noise to the model so we should ignore it here)

@@

**Initial thoughts - Transect**

  - all but one correctly classified (one Transition looked like Upland) 
  - sulfate is interesting, maybe the relative transition in redox is more consistent than the relative transition in other things across CB and WLE sites 
  - neither horizon nor region is important to this model

@@

**Initial thoughts - Site**

  - All correctly identified
  - NO3 and TN as top variables followed by region and horizon seems like a nice mix! Much less "one variable to rule them all" vibes
  - Transect not important to this model
